My title

### 2022-03-21 outputs/paper/paper.Rmd
Title space
Mistake
Add results for crime count

```{r crime-plot, echo=FALSE, warning=FALSE, message = FALSE, fig.height=6, fig.width=8}
subset_data = gss_data %>% filter(msvic < 900)  # ignore invalid responses
subset_data %>% 
  left_join(as.data.frame(list(msvic=msvic_num, msvic_label=msvic_labels))) %>%
  ggplot(aes(as.factor(msvic_label), fill=msvic_label)) + geom_histogram(stat="count") + 
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) + xlab("Crime") +
  labs(title = "Crime Count", fill="Crime Category")
```

```{r crime-count-plot-by-education, echo=FALSE, warning=FALSE, message = FALSE, fig.height=6, fig.width=8}
# university_crime_count
grid.arrange(university_crime_count,
            college_crime_count,
            elementary_crime_count,
            nrow=1)
```

>>>>

## Crime By Category

```{r crime-plot, fig.cap="Crime Count By Category", echo=FALSE, warning=FALSE, message = FALSE, fig.height=6, fig.width=8}
subset_data = gss_data %>% filter(msvic < 900)  # ignore invalid responses
subset_data %>% 
  left_join(as.data.frame(list(msvic=msvic_num, msvic_label=msvic_labels))) %>%
  ggplot(aes(as.factor(msvic_label), fill=msvic_label)) + geom_histogram(stat="count") + 
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
  labs(title = "Crime Count", fill="Crime Category")
```

Figure \@ref(fig:crime-plot) shows the crime count of different categories. 
We can identify the crimes that happen the most frequently.

Theft, assault, and break and enter happen most frequently.

### Crime Count By Education Level

```{r crime-count-plot-by-education, fig.cap="Crime By Education Level", echo=FALSE, warning=FALSE, message = FALSE, fig.height=6, fig.width=8}
# university_crime_count
grid.arrange(university_crime_count,
            college_crime_count,
            elementary_crime_count,
            nrow=1)
```

Figure \@ref(fig:crime-count-plot-by-education) show the same crime count but differentiated by education level.

The education levels are mutually exclusive (i.e. if a respondent select "Yes" for "Elementary/junior/high school" education level, then he/she can not select "Yes" for the other 2 questions). The 3 plots all have similar shapes to Figure \@ref(fig:crime-plot), i.e. the most frequent crime categories in Figure \@ref(fig:crime-plot) are also the most frequent crimes in Figure \@ref(fig:crime-count-plot-by-education).

Within Figure \@ref(fig:crime-count-plot-by-education), the subplot "University Education Crime Count" has a obviously different shape from the other 2 education level.

It seems like samples with University Education have higher chance of getting "Sexual Assault" and "Theft of personal property".
